Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-05 trunk/SAiP/Module1/H1/doc/paper.tex
Document update

% =====================================================================
\section{Architectural Requirements}

@@

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 700 350,scale=0.4]{figures/deployment.pdf}}
\caption{HS07 Allocation Diagram}
\label{fig:allocation}
\end{figure}

@@

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{itemize}
\item \emph{Stakeholders and their concerns}. This encompasses both users/aquirers and developers. \item \emph{Ffeasibility}
\item \emph{Maintainablity}
\item \emph{Security} How is the Gateway protected? What protection is there against attack and inproper use? 
\item \emph {Safety} How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item \emph{Availability} What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item \emph{Testability} What is the tesability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{itemize}

@@

\cite{perrywolf1992} defines "elements" as three different classes, data elements, processing elements and connecting elements. In HS07 the data elements are temperatures, the processing element is the gateway and the connecting element is HTTP. The "form", as described by Perry and Wolf, is the choice of the observer pattern in HS07, and the "rationale" for doing so are defined by the Achitectural Requirements described elsewhere in this document.

>>>>

% =====================================================================
\section{Architectural Requirements}
\label{sec:requirements}

@@

Figure~\ref{fig:allocation_pc} shows the setup as specified in the build-file
where all HS07 processes are located on the same node. As can be seen in the
figure the gateway can be accessed from one or more PC through an internet
connection.

\begin{figure}[!htb]
\center {\includegraphics[scale=0.4]{figures/deployment.pdf}}
\caption{HS07 Allocation Diagram showing deployment on a PC}
\label{fig:allocation_pc}
\end{figure}

Figure~\ref{fig:allocation_actual} shows a more realistic example of a deployment
where thermometers and radiators are seperate nodes that are connected to
the gateway through a LAN connection.

\begin{figure}[!htb]
\center {\includegraphics[viewport=110 200 600 420, scale=0.4]{figures/deployment_actual.pdf}}
\caption{HS07 Allocation Diagram showing deployment on seperate nodes}
\label{fig:allocation_actual}
\end{figure}

@@

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{itemize}
\item \emph{Stakeholders and their concerns}. This encompasses both users/aquirers and developers.
\item \emph{Feasibility}
\item \emph{Maintainablity}
\item \emph{Security} How is the Gateway protected? What protection is there against attack and inproper use? 
\item \emph {Safety} How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item \emph{Availability} What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item \emph{Testability} What is the tesability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{itemize}

@@

\cite{perrywolf1992} defines "elements" as three different classes, data elements,
processing elements and connecting elements. In HS07 the data elements are
temperatures, the processing element is the gateway and the connecting element
is HTTP. The "form", as described by Perry and Wolf, is the choice of the observer
pattern in HS07.

The "rationale" described in \cite{perrywolf1992} captures the reasons for choices
made when defining the architecture. In this architectural description a rationale
would e.g. document the choice of using HTTP as the protocol between the components. A
Rationale is not part of this document.
